The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
temporal scale subsections

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou. Caribou therefore have
greater access to forage in snow-free seasons. We  partitioned data into two
discrete seasons: summer (3 August - 20 September) and winter (1 January – 17
February) based on caribou socioecology [@Peignier_2019].

@@

### Temporal scale
<!--TODO: are we missing some mention of 2017 summer and 2018 winter somewhere?-->
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (starting at 1
January) and summer (starting at 3 August). The position of the time window was
shifted by 1-48 days, using a fixed time window length of 48 days. These new
time windows were iteratively used to partition data into two discrete seasons
(winter, summer) and generate multilayer networks.

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. In addition to altering the temporal scale by
adjusting the time window, we investigated the influence of the number of
observations on resulting multilayer networks. We randomly selected 500
timesteps and iteratively included 25 additional observations, regenerating the
multilayer network and calculating associations of individuals. Subsequent
iterations included the previous set of observations to mimic observational
data. <!-- TODO: bah conclude / this sentence falls off a cliff -->

>>>>

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou. Caribou therefore have
greater access to forage in snow-free seasons. We  partitioned data into two
discrete seasons: summer (3 August - 20 September 2017) and winter (1 January – 17
February 2018) based on caribou socioecology [@Peignier_2019].

@@

### Temporal scale
#### Time window length and position
We altered the temporal scale of multilayer networks by varying the length and
position of the time window used to define seasons. The length of the time
window varied from 40-100 days using a fixed start day for winter (starting at 1
January) and summer (starting at 3 August). The position of the time window was
shifted by 1-48 days, using a fixed time window length of 48 days. These new
time windows were iteratively used to partition data into two discrete seasons
(winter, summer) and generate multilayer networks.

#### Number of observations
Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. In addition to altering the temporal scale by
adjusting the time window, we investigated the influence of the number of
observations on resulting multilayer networks. We randomly selected 500
timesteps and iteratively included 25 additional observations, regenerating the
multilayer network and calculating associations of individuals. Subsequent
iterations included the previous set of observations to mimic observational
data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
